---
title: "AGA 2015 PDT Conference"
subtitle: "Attendee List"
author: "FI Consulting"
date: "July 12, 2015"
output: 
  ioslides_presentation:
    logo: logo_slides.png
    transition: faster
    widescreen: yes
---

<style>
slide{background-color:white;}
td{font-size:14px;}
article{color:black;}
</style>


```{r setup, include=FALSE}

require(knitr)
require(DT)
require(dplyr)
require(googleVis)
require(stringr)
require(scales)
require(png)
require(grid)
require(leaflet)



load('PDT_2015.RData')

op <- options(gvis.plot.tag='chart')
opts_chunk$set(echo = FALSE, results='asis', size="small", fig.align='center')


```


# Attendees Search

---

Filter/Sort by Attendee Name, Title, Organization, City, or State
```{r search}

datatable(
  select(final, state, loc, name, title, company), 
  colnames = c('State', 'City', 'Name', 'Title', 'Organization'),
  class = 'row-border stripe compact order-column hover',
  options=list(pageLength = 10, lengthMenu = c(5, 10, 15, 20)),
  rownames=FALSE)

```

# Attendance by Geographic Location

----

Number of Attendants by City 
```{r leaflet}
map.dat <- agg.city %>%
  filter(!is.na(city)) %>%
  mutate(Tip = paste(city, Attendees, sep = " : ")) 

# bounds
bounds <- map.dat %>% 
  filter(!grepl('GU|AK|HI',state)) %>% 
  ungroup() %>% 
  summarize(lon1 = min(lon),
            lon2 = max(lon),
            lat1 = min(lat),
            lat2 = max(lat))


leaflet(data = map.dat,
        width = 800, height = 450) %>% 
  addTiles() %>%
  fitBounds(bounds$lon1,bounds$lat1,bounds$lon2,bounds$lat2) %>% 
  addProviderTiles("CartoDB.Positron") %>%
  # addMarkers(~long, ~lat, popup = ~Tip) 
  addCircleMarkers(
    ~lon, ~lat, popup = ~Tip,
    radius = ~sqrt(Attendees)*2,
    color = 'green',
    stroke = FALSE, fillOpacity = 0.5)

```


## Attendance by State
```{r geo, fig.align='center'}

#top States data
dat.st<- agg.state %>%
  mutate(pct = Attendees/sum(Attendees),
         state = ifelse(pct>.02,state, 'Other'),
         state = ifelse(is.na(state),'Other',state)) %>%
  group_by(state) %>%
  summarise(Attendees = sum(Attendees)) %>%
  arrange(-Attendees)


# States Map
GeoStates <- gvisGeoChart(
  data = filter(agg.state, !is.na(state)), 
  "state", "Attendees",
  options=list(region="US", magnifyingGlass.enable=T, 
               displayMode="regions", 
               resolution="provinces",
               width=800, height=500))

plot(GeoStates)


```

---

```{r}
# Top States Pie chart

#top States data
dat.st<- agg.state %>%
  mutate(pct = Attendees/sum(Attendees),
         state = ifelse(pct>.05,state, 'Other'),
         state = ifelse(is.na(state),'Other',state)) %>%
  group_by(state) %>%
  summarise(Attendees = sum(Attendees)) %>%
  arrange(-Attendees)


Pie <- gvisPieChart(
  dat.st,
  options=list(
    title="Attendees by State",
    titleTextStyle="{fontSize:20}",
    legend = "{position: 'top', fontSize:10}",
    pieSliceText = 'label',
    width=800, height=500,
    pieHole=0.35
  )
)

plot(Pie)

```

---

```{r}
#Top Cities Bar Plot

#top Cities data
dat.city<- 
  ungroup(agg.city) %>%
  select(city, Attendees) %>%
  filter(!is.na(city)) %>% 
  top_n(n = 10,wt = Attendees) %>% 
  arrange(-Attendees)


Bar <- gvisBarChart(dat.city, options = list(
  series = "[{color: 'red'}]",
  titleTextStyle="{fontSize:20}",
  width=800,height=500, legend='none', 
  title="Top Cities"))
plot(Bar)

```



# Attendees' Certifications, Degrees, and other Designations  

---

```{r designations}

agg.certs <-  
  str_split(final$desig, ', *') %>% 
  unlist() %>% 
  gsub('-Retired|-Retir','',x = .) %>% 
  gsub('PhD','Ph.D.', x = .) %>% 
  data.frame(desig=.,stringsAsFactors = F) %>% 
  filter(!is.na(desig) & desig!='CIA') %>% 
  group_by(desig) %>%
  summarize(Count=n()) %>%
  arrange(-Count)


agg.certs.top <- 
  agg.certs %>%
  mutate(Pct = Count/nrow(final),
         desig = ifelse(Pct<.03, 'Other', desig)) %>%
  group_by(desig) %>%
  summarize(Count = sum(Count),
            Pct = round(Count/nrow(final),2)) %>%
  arrange(-Count) %>%
  select(-Count) 


Bar1 <- gvisBarChart(
  agg.certs, 
  options = list(
    title="Number of Attendees by Designation",
    titleTextStyle="{fontSize:28}",
    fontSize = 11,
    width=1100, height=600, 
    legend='none'))

plot(Bar1)
```


---

```{r designations_2}
Bar2 <- gvisColumnChart(
  agg.certs.top, 
  options = list(
    legend='none',
    series = "[{color: 'red'}]",
    titleTextStyle="{fontSize:20}",
    vAxes="[{title:'Percent of all attendees',
             format:'#,###%',
             textPosition: 'out'}]",
    width=800,height=600, legend='none', 
    title="% of Total"))

plot(Bar2)
```


# Most frequent Job Titles and Organizations

---

Job Titles  
```{r cloud, fig.width=6, fig.height=6}
img <- readPNG('wordcloud_title.png')
grid.raster(img)
```

---

Organizations  
```{r cloud2, fig.width=6, fig.height=6}
img <- readPNG('wordcloud_org.png')
grid.raster(img)
```

## Data Source
Official attendee list can be downloaded from [here](https://www.agacgfm.org/AGA/PDT2014/documents/AttendeeList.pdf)
